Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-12 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
corrected space 4 pages now

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions&nbsp;\cite{Frery1997}. 
The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Yue2021}.
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align}
where $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
In&nbsp;\eqref{E:gamma1}, $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,

@@

In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}

@@

save(results_gi0, file = "./Data/results_gi0.Rdata")

@@

load("./Data/results_gi0.Rdata")

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/results_gi0.Rdata")

@@

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

for (L in L_values) {
  load(paste0("./Data/results_", L, ".Rdata"))

@@

load("./Data/results_2.Rdata")
summary_stats_2 <- all_summary_stats[["2"]]

# load("./Data/results_5.Rdata")
# summary_stats_5 <- all_summary_stats[["5"]]

load("./Data/results_8.Rdata")
summary_stats_8 <- all_summary_stats[["8"]]

@@

# Load saved results
load("./Data/results_2.Rdata")
load("./Data/results_5.Rdata")
load("./Data/results_8.Rdata")
load("./Data/results_18.Rdata")

@@

save(results, file = "./Data/type_I_results.Rdata")

@@

results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")

@@

load("./Data/type_I_results.Rdata")

@@

load("./Data/results_power.Rdata")

@@

# 
save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test.Rdata")

@@

# 
load("./Data/sim_empirical_test.Rdata")

>>>>

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions. The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Yue2021}.
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align}
where $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
In&nbsp;\eqref{E:gamma1}, $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,

@@

In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma1}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}

@@

save(results_gi0, file = "./Data/resultsgi0.Rdata")

@@

load("./Data/resultsgi0.Rdata")

@@

```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/resultsgi0.Rdata")

@@

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results1_", L, ".Rdata"))
}

@@

for (L in L_values) {
  load(paste0("./Data/results1_", L, ".Rdata"))

@@

load("./Data/results1_2.Rdata")
summary_stats_2 <- all_summary_stats[["2"]]

# load("./Data/results1_5.Rdata")
# summary_stats_5 <- all_summary_stats[["5"]]

load("./Data/results1_8.Rdata")
summary_stats_8 <- all_summary_stats[["8"]]

@@

# Load saved results
load("./Data/results1_2.Rdata")
load("./Data/results1_5.Rdata")
load("./Data/results1_8.Rdata")
load("./Data/results1_18.Rdata")

@@

save(results, file = "./Data/type_I_results1.Rdata")

@@

results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power1.Rdata")

@@

load("./Data/type_I_results1.Rdata")

@@

load("./Data/results_power1.Rdata")

@@

# 
save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test1.Rdata")

@@

# 
load("./Data/sim_empirical_test1.Rdata")
